E exp 3

### 2018-08-19 experiments/E_exp_3/writeup/E_exp_3.Rmd
minor edit to e3

```{r, "Full table of instructions", echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Target, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Target, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='ccccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

>>>>

```{r, "Full table of instructions", echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Target, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Target, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
instructions_table %>% 
  kable(align='ccccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```
